On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-04 paper/cav_determinisim_main.tex
overall worst case added to max variance def

The maximum variance over the entire set of $n$ repeated simulations is defined as the largest variance of any actor at any time in any of the simulation runs, as given in Equation~\ref{eq:max_sigma}. 
%{\color{red} This is still a function over time - should it be?}
\begin{equation} \label{eq:max_sigma}
\max_{a,t}\sigma_a^{2}(t)
\end{equation}
The maximum deviation is the square root of the maximum variance {\color{red} The absolute value of the square root?} and herein referred to as ${\max\sigma}$ for brevity. {\color{red} So, ``a'' is any actor or a specific actor? Likewise, ``t'' is any time point or a specific time point? NOTE that any actor any time means a in A and t in T, where A is the set of actors and T is the set of all time points.}

@@

\subsection{Initial Results and Discussion}\label{ResultsSection}

@@

% ***************************************************
%  Results and Discussion
% ***************************************************
\subsection{Final Results and Discussion}\label{ResultsSection}

>>>>

The maximum variance over the entire set of $n$ repeated simulations, i.e.\ the overall observed worst case, is defined as the largest variance of any actor at any time in any of the simulation runs, as given in Equation~\ref{eq:max_sigma}. 
%{\color{red} This is still a function over time - should it be?}
\begin{equation} \label{eq:max_sigma}
\max_{a,t}\sigma_a^{2}(t)
\end{equation}
The maximum deviation is the square root of the maximum variance {\color{red} The absolute value of the square root?} and herein referred to as ${\max\sigma}$ for brevity. {\color{red} So, ``a'' is any actor or a specific actor? Likewise, ``t'' is any time point or a specific time point? NOTE that any actor any time means a in A and t in T, where A is the set of actors and T is the set of all time points.}

@@

\subsection{Initial Results and Discussion}\label{InitialResultsSection}

@@

% ***************************************************
%  Results and Discussion
% ***************************************************
\subsection{Final Results and Discussion}\label{FinalResultsSection}
